03 Data Vizualization

### 2022-03-29 02_LH-SIP_Quantification.Rmd
added weighting

---
title: "01_LH-SIP_Quantification"
author: "Tristan Caro"
date: "3/23/2022"
output: html_document
---

@@

```{r}
# Create a summarized dataframe grouped by experimental replicates
turnover_summarized <- turnover %>% 
  group_by(
    time_course,
    terrain, 
    inc_time_d, 
    compound
  ) %>% 
  summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

@@

weighted_time_course <- LH_SIP_data_summarized %>%
  group_by(
    terrain, 
    inc_time_d
  ) %>% 
  dplyr::summarize(
    # Weight at2H
    at2H_weighted = 
      sum(at2H * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE),
    # Weight `2F_alk`
    `2F_alk_weighted` = 
      sum(`2F_alk` * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE),
    # Keep these:
    f_label = mean(F_label_mn, na.rm = TRUE),
    a = 0.6,
    t0 = 0,
    d_t = inc_time_d - t0, # change in time
    f_start = mean(at2H_mn_zero, na.rm = TRUE),
    f_t = `2F_alk_weighted`,
    dF = `2F_alk_weighted` - f_start
  ) %>%
  dplyr::summarize_if(
    is.numeric,
    mean,
    na.rm = TRUE
  ) %>%
  mutate(
    u_d_weighted = calculate_turnover(
      a = a,
      FT = f_t,
      F0 = f_start,
      FL = f_label,
      t = d_t
    ),
    gen_d_weighted = turnover_to_gen(u_d_weighted)
  )
```

@@

>>>>

---
title: "02_LH-SIP_Quantification"
author: "Tristan Caro"
date: "3/23/2022"
output: html_document
---

@@

```{r}
# Create a summarized dataframe grouped by experimental replicates
turnover_summarized <- turnover %>% 
  group_by(
    time_course,
    terrain, 
    inc_time_d,
    compound
  ) %>% 
  dplyr::summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

@@

weighted_time_course <- LH_SIP_data_summarized %>%
  group_by(
    terrain, 
    inc_time_d
  ) %>% 
  dplyr::summarize(
    # Weight at2H
    at2H_weighted = 
      sum(at2H * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE),
    # Weight `2F_alk`
    `2F_alk_weighted` = 
      sum(`2F_alk` * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE),
    # Keep these:
    f_label = mean(F_label_mn, na.rm = TRUE),
    a = 0.6,
    t0 = 0,
    d_t = inc_time_d - t0, # change in time
    f_start = mean(at2H_mn_zero, na.rm = TRUE),
    f_t = `2F_alk_weighted`,
    dF_weighted = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),
  ) %>%
  dplyr::summarize_if(
    is.numeric,
    mean,
    na.rm = TRUE
  ) %>%
  mutate(
    u_d_weighted = calculate_turnover(
      a = a,
      FT = f_t,
      F0 = f_start,
      FL = f_label,
      t = d_t
    ),
    gen_d_weighted = turnover_to_gen(u_d_weighted)
  )
```

@@

turnover_summarized %>% saveRDS(file = "cache/turnover_summarized")

### 2022-03-29 03_data_viz.Rmd
added weighting

---
title: "Paper Figures"
author: "Tristan Caro"
date: "`r Sys.Date()`"
output:
    html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

@@

@@

## Figure: Microbial turnover rate across soil types

@@

## Figure: Phyla FA profiles

@@

## Figure: Weighted turnover time

@@

## Figure: Compound abundance vs. turnover

>>>>

---
title: "03 Data Vizualization"
author: "Tristan Caro"
date: "`r Sys.Date()`"
output:
    html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

@@

# Summarized turnover

turnover_summarized <- readRDS("cache/turnover_summarized")

@@

## Microbial turnover rate across soil types

@@

## Phyla FA profiles

@@

## dF

```{r}
p_dF <- turnover_summarized %>% 
  filter(time_course == "0d -->") %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF, dF_weighted),
    values_to = "dF", 
    names_to = "type"
  ) %>% view()

  ggplot(
    aes(
      x = inc_time_d,
      y = dF
    )
  ) +
  # Weighted data here:
  geom_line(aes(
    x = inc_time_d,
    y = dF_weighted,
    color = terrain),
    size = 1.5,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      x = inc_time_d,
      y = dF_weighted,
      color = terrain,
      fill = terrain),
    size = 2,
    alpha = 0.5
    ) +
  # Unweighted data here:
  geom_borderline(
    data = turnover_summarized,
    aes(group = compound),
    color = "gray"
) +
  geom_point(
    data = turnover_summarized,
    size = 2,
    alpha = 0.5
    ) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(
    xlim = c(0, 8),
    clip = "off"
    ) +
  facet_wrap(vars(terrain),
             nrow = 1) +
  labs(x = "Incubation Time (Days)",
       y = TeX("$ \\Delta ^2H$ (at%)"),
       ) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))

p_dF
```

@@

## Compound abundance vs. turnover
